The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-05 article.tex
Quick capitalization on authors fix

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as adi et al where a DNA clone resistant approach is taken throughout\cite{adi2009mechatronic}; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is the HSE which is used to verify other parts of the system much like adi et al\cite{adi2009mechatronic}.

@@

@@

Other planning algorithms use specialized planning based on a sub process task such as ahn et al's vertical control system, where one module is independently responsible to avoiding objects while more abstract modules can plan according to behavior of objects\cite{ahn2008robust}. Such planning can also be implemented into a map of acceptable behaviors for each state. Multiple goal resolution is attractive as it may still be used in the evaluation of an observed behavior, we will however demonstrate the concept through an avoidance task.

@@

>>>>

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as Adi et al where a DNA clone resistant approach is taken throughout\cite{adi2009mechatronic}; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is the HSE which is used to verify other parts of the system much like Adi et al\cite{adi2009mechatronic}.

@@

REMOVED EXPANDED EKF/UKF DISCUSSION

@@

Other planning algorithms use specialized planning based on a sub process task such as Ahn et al's vertical control system, where one module is independently responsible to avoiding objects while more abstract modules can plan according to behavior of objects\cite{ahn2008robust}. Such planning can also be implemented into a map of acceptable behaviors for each state. Multiple goal resolution is attractive as it may still be used in the evaluation of an observed behavior, we will however demonstrate the concept through an avoidance task.

@@

REMOVED LENGTHY COORDINATE FRAME DESCRIPTIONS FROM HERE
